\textbf{SPECFEM3D}\\ \textbf{Cartesian}\\ \textbf{User Manual}

### 2018-11-07 doc/USER_MANUAL/06_fault_sources.tex
Revised the USER_MANUAL and added an mesh example (scripts for CUBIT meshing)

\&\textbf{RUPTURE\_SWITCHES}  /
RATE\_AND\_STATE ,TPV16 ,HETE\_RSF ,TPV10X

@@

@@

\begin{lyxlist}{00.00.0000}
\item [{\&\textbf{RUPTURE\_SWITCHES}}] input block sets some switches in the simulation process.
  \begin{description}
    \item [{RATE\_AND\_STATE}]
         = .TRUE. use rate and state friction,=.FALSE. use slip weakening friction
    \item [{TPV16}]
         =.TRUE turn on heterogeneity fault property input for slip weakening friction from DATA\/input\_file.txt,
         =.FALSE. turn off such feature
    \item [{HETE\_RSF}]
         =.TRUE. turn on heterogeneity fault property input for rate and state friction
              using input from DATA\/rsf\_hete\_input\_filr.txt,
   =.FALSE. turn off such feature
    \item[{TPV10X}]
         =.TRUE. turn on some ad hoc features for TPV101-104 simulations, a rate strengthening
   layer surrounding the rate weakening region.
   =.FALSE. turn off such feature
   \end{description}

@@

>>>>

\&\textbf{RUPTURE\_SWITCHES}  /
RATE\_AND\_STATE ,TPV16 ,HETE\_RSF ,TPV10X ,TWF

@@

\&\textbf{TWF} nuc\_x, nuc\_y, nuc\_z, nuc\_r, nuc\_t0, nuc\_v /

@@

\begin{lyxlist}{00.00.0000}
\item [{\&\textbf{RUPTURE\_SWITCHES}}] input block sets some switches in the simulation process.
  \begin{description}
    \item [{RATE\_AND\_STATE}]
         = .TRUE. use rate and state friction,=.FALSE. use slip weakening friction
    \item [{TPV16}]
         =.TRUE turn on heterogeneity fault property input for slip weakening friction from DATA\/input\_file.txt,
         =.FALSE. turn off such feature
    \item [{HETE\_RSF}]
         =.TRUE. turn on heterogeneity fault property input for rate and state friction
              using input from DATA\/rsf\_hete\_input\_filr.txt,
   =.FALSE. turn off such feature
    \item[{TPV10X}]
         =.TRUE. turn on some ad hoc features for TPV101-104 simulations, a rate strengthening
   layer surrounding the rate weakening region.
   =.FALSE. turn off such feature
    \item[{TWF}]
         =.TRUE. turn on time-weakening nucleation. This function is activated only when                    
         RATE\_AND\_STATE=.FALSE. and TWF=.TRUE.
   \end{description}

@@

\item [{\&\textbf{TWF}}] input block sets the time-weakening friction parameters
of the fault:
\begin{description}
\item [{nuc\_x}]  = x coordinate of the hypocenter (in m)
\item [{nuc\_y}]  = y coordinate of the hypocenter (in m)
\item [{nuc\_z}]  = z coordinate of the hypocenter (in m)
\item [{nuc\_r}]  = the radius of time-weakening nucleation (in m) 
\item [{nuc\_t0}] = the cohesive time. The friction linearly decreases from static friction to dynamic friction during this time (in s)
\item [{nuc\_v}]  = the time-weakening nucleation speed (in m/s)
\end{description}
